---
title: "OTB regulatory assessment"
author: "M. W. Beck"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
---
  
```{r setup, warning = F, message = F}
library(knitr)
library(tidyverse)
library(tbeptools)
library(here)
library(lubridate)
library(reactable)

opts_chunk$set(warning = FALSE, message = FALSE)

load(file = here('data/epcdata.RData'))
load(file = here('data/phydata.RData'))

yrrng <- c(2000, 2020)
```

```{r}
trgs <- targets

bay_segment <- 'OTB'
param <- 'chla'
avedat <- anlz_avedat(epcdata, partialyr = F) %>%
  .$ann

wqdat <- avedat %>%
  dplyr::filter(yr >= yrrng[1] & yr <= yrrng[2]) %>%
  dplyr::filter(bay_segment %in% !!bay_segment) %>%
  dplyr::filter(var %in% !!paste0('mean_', param)) %>%
  dplyr::left_join(trgs, by = 'bay_segment') %>%
  dplyr::select(bay_segment, yr, var, val, thresh = !!paste0(param, '_thresh'), target = !!paste0(param, '_target')) %>%
  dplyr::mutate(
    bay_segment = factor(bay_segment, levels = c('OTB', 'HB', 'MTB', 'LTB')),
    thr = dplyr::case_when(
      val < thresh ~ 'green',
      val >= thresh ~ 'red'
    ), 
    trg = dplyr::case_when(
      val < target ~ 'green', 
      val >= target ~ 'red'
    )
  )

totab <- wqdat %>% 
  select(-bay_segment, -var)
```

Annual assessment of chlorophyll-a in Old Tampa Bay achieving the regulatory threshold or management target (green = achieved, red = not achieved).  Water quality data from Environmental Protection Commission of Hillsborough County.

```{r}
reactable(totab, 
  columns = list(
      yr = colDef(name = 'Year'), 
      val = colDef(name = 'Ann. mean Chl-a ($\\mu$g/L)', format = colFormat(digits = 1)), 
      thresh = colDef(name = 'Regulatory threshold'), 
      target = colDef(name = 'Management target'), 
      thr = colDef(name = 'Regulatory category'), 
      trg = colDef(name = 'Managment category')
    ), 
  resizable = T, showSortable = T, 
  defaultPageSize = nrow(totab), 
  showPageSizeOptions = F
  ) 
```

```{r}
otbsta <- stations %>% 
  filter(bay_segment == 'OTB') %>% 
  pull(epchc_station)

phydat <- phydata %>% 
  filter(name %in% 'Pyrodinium bahamense') %>% 
  filter(epchc_station %in% otbsta) %>% 
  mutate(
    count = count * 1e4, # /0.1mL to /L
    val = case_when(
      count >= 1e6 ~ 'high',
      count < 1e6 & count >= 1e5 ~ 'medium', 
      T ~ 'other'
    )
  ) %>% 
  group_by(yr) %>% 
  summarise(
    hval = sum(val == 'high'), 
    mval = sum(val == 'medium'),
    .groups = 'drop'
  )

totab <- wqdat %>% 
  select(yr, thr, trg) %>% 
  left_join(phydat, by = 'yr') %>% 
  mutate(
    hval = ifelse(is.na(hval), 0, hval),
    mval = ifelse(is.na(mval), 0, mval)
    )
```

Comparison of annual assessment of chlorophyll-a in Old Tampa Bay with *P. bahamense* cell concentrations.  Phytoplankton data from Environmental Protection Commission of Hillsborough County.

```{r}
reactable(totab, 
  columns = list(
      yr = colDef(name = 'Year'), 
      thr = colDef(name = 'Regulatory category'), 
      trg = colDef(name = 'Managment category'), 
      hval = colDef(name = 'Counts when P. bahamense > 1e6 cells/L'),
      mval = colDef(name = 'Counts when P. bahamense > 1e5, < 1e6 cells/L')
    ), 
  resizable = T, showSortable = T, 
  defaultPageSize = nrow(totab), 
  showPageSizeOptions = F
  ) 
```
